---
title: "Teachers"
output: html_document
date: "2022-10-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LIBRARIES

```{r}
library(RSQLite)
library(DBI)
library(dplyr)
```

## IMPORT

```{r}
con <- dbConnect(SQLite(), "/Users/User/Documents/Teachers/teachers.db")
```

## DATA

### IQ Score 2022

Source: <https://worldpopulationreview.com/country-rankings/average-iq-by-country>

```{r}
iq_country199 <- dbGetQuery(con,
                           "select country, iq from iq;")
iq_country199
```

```{r}
write.csv2(iq_country199, "199countries_iqscore.csv", sep = ";")
```

Plot (lollipop-h)

### PISA Score 2018

PISA measures 15-year-olds' ability to use their reading, mathematics and science knowledge and skills to meet real-life challenges. The objective of PISA is to measure the “yield” of education systems, or what skills and competencies students have acquired and can apply in reading, mathematics, and science to real-world contexts by age 15.
Source : <https://worldpopulationreview.com/country-rankings/pisa-scores-by-country>

```{r}
pisa_score78 <- dbGetQuery(con, 
                           "select country_name
                           , reading_mean reading
                           , math_mean math
                           , science_mean science 
                           from pisa_score;")
pisa_score78
```

```{r}
ranked_pisascore78 <- pisa_score78 %>% 
  mutate(rank_reading = order(order(reading, decreasing = T))) %>%
  mutate(rank_math = order(order(math, decreasing = T))) %>%
  mutate(rank_science = order(order(science, decreasing = T)))
ranked_pisascore78
```

```{r}
write.(ranked_pisascore78, "79countries_rankedpisa.csv", sep = ";")
```

Horizontal Stacked Bar Chart

### Government Spending on Education varying 2016 to 2021

Government expenditure is defined as all government spending in an economy. Government expenditure consists of two parts, current government expenditure and capital government expenditure: Current expenditure - government spending on the day-to-day operations of government, for example the costs of running a hospital. Government purchases are expenditures on goods and services by federal, state, and local governments. The combined total of this spending, excluding transfer payments and interest on the debt, is a key factor in determining a nation's gross domestic product (GDP).
Source: <https://ourworldindata.org/grapher/share-of-education-in-government-expenditure?tab=table>

```{r}
government_expenditure192 <- dbGetQuery(con, 
                                        "select country_id, country_name, 
                                        max(year) as latest_year,
                                        percent_total_expenditure from expenditure
                                        group by country_id;")
government_expenditure192
```

```{r}
write.csv2(government_expenditure192, "192countries_govexpend.csv", sep = ";")
```

Vertical Bar Chart

### Education Gap 2021 for HLS, 2022 for Student, Teacher, School

```{r}
edu_gap_idn <- dbGetQuery(con, 
                          "select sc.no, sc.prov_name
                          , sc.sd_total+sc.smp_total+sc.sma_total school
                          , st.sd_total+st.smp_total+st.sma_total student
                          , tc.sd_total+tc.smp_total+tc.sma_total teacher
                          , hls.angka_hls, hls.rata_lama_sekolah
                          from school_idn sc
                          join student_idn st on st.prov_name = sc.prov_name
                          join teacher_idn tc on tc.prov_name = sc.prov_name
                          join hls_id hls on hls.prov_name = sc.prov_name
                          where sc.no is not '';")
edu_gap_idn
```

```{r}
write.csv2(edu_gap_idn, "34provinces_edugap.csv", sep = ";")
```

Map chart

### Salary 2021

```{r}

```


### Regression Data

```{r}
reg_data <- dbGetQuery(con, 
                       "select s.country_id, s.country_name
                        , avg(s.salary) salary
                        , e.expenditure_percapita
                        , d.percent_total_expenditure gov_expenditure
                        , n.`2020` as net_user
                        , h.expected_school
                        , h.years_school
                        , p.reading_mean
                        , p.math_mean
                        , p.science_mean
                        , i.country_index 
                        from salary s
                        join expenditure_percapita e on e.country_id = s.country_id
                        join net_users n on n.country_id = s.country_id
                        join hdi_country h on h.country_id = s.country_id
                        inner join pisa_score p on p.country_id = s.country_id
                        inner join edu_index i on i.country_id = s.country_id
                        inner join expenditure d on d.country_id = s.country_id
                        group by s.country_id;")
reg_data
```

```{r}
# https://etateach.com/teacher-salaries-around-the-world.html#Argentina
reg_data['salary'][reg_data['country_id'] == 'ARG'] = 9647

# https://etateach.com/teacher-salaries-around-the-world.html#Australia
reg_data['salary'][reg_data['country_id'] == 'AUS'] = 62300

# https://etateach.com/teacher-salaries-around-the-world.html#Austria
reg_data['salary'][reg_data['country_id'] == 'AUT'] = 45807.35

# https://www.salaryexpert.com/salary/job/teacher/brazil
reg_data['salary'][reg_data['country_id'] == 'BRA'] = 16748.51

# https://etateach.com/teacher-salaries-around-the-world.html#Canada
reg_data['salary'][reg_data['country_id'] == 'CAN'] = 55345

# https://etateach.com/teacher-salaries-around-the-world.html#Switzerland
reg_data['salary'][reg_data['country_id'] == 'CHE'] = 99302

# https://www.salaryexpert.com/salary/job/teacher/chile
reg_data['salary'][reg_data['country_id'] == 'CHL'] = 18194.714

# https://www.salaryexpert.com/salary/job/teacher/china
reg_data['salary'][reg_data['country_id'] == 'CHN'] = 25788.78
reg_data['expenditure_percapita'][reg_data['country_id'] == 'CHN'] = 4698.876

# https://etateach.com/teacher-salaries-around-the-world.html#Colombia
reg_data['salary'][reg_data['country_id'] == 'COL'] = 9684

# https://www.salaryexpert.com/salary/job/teacher/costa-rica
reg_data['salary'][reg_data['country_id'] == 'CAN'] = 19112.28

# https://id.indeed.com/career/guru/salaries
reg_data['salary'][reg_data['country_id'] == 'CRI'] = 4724.24

reg_data
```

```{r}
# https://etateach.com/teacher-salaries-around-the-world.html#Czechia
reg_data['salary'][reg_data['country_id'] == 'CZE'] = 12203

# https://www.salaryexpert.com/salary/job/teacher/denmark
reg_data['salary'][reg_data['country_id'] == 'DNK'] = 55184

# https://etateach.com/teacher-salaries-around-the-world.html#Estonia
reg_data['salary'][reg_data['country_id'] == 'EST'] = 19061.22

# https://www.salaryexpert.com/salary/job/teacher/brazil
reg_data['salary'][reg_data['country_id'] == 'FRA'] = 16748.51

# https://etateach.com/teacher-salaries-around-the-world.html#Hungary
reg_data['salary'][reg_data['country_id'] == 'HUN'] = 15564

# https://etateach.com/teacher-salaries-around-the-world.html#Indonesia
reg_data['salary'][reg_data['country_id'] == 'IDN'] = 4630.32

# https://etateach.com/teacher-salaries-around-the-world.html#Iceland
reg_data['salary'][reg_data['country_id'] == 'ISL'] = 41989.44

# https://etateach.com/teacher-salaries-around-the-world.html#Israel
reg_data['salary'][reg_data['country_id'] == 'ISR'] = 47568

# https://etateach.com/teacher-salaries-around-the-world.html#Japan
reg_data['salary'][reg_data['country_id'] == 'JPN'] = 36384
reg_data['expenditure_percapita'][reg_data['country_id'] == 'JPN'] = 10404.085

# https://www.salaryexpert.com/salary/job/teacher/luxembourg
reg_data['salary'][reg_data['country_id'] == 'LUX'] = 60394.64

# https://etateach.com/teacher-salaries-around-the-world.html#Latvia
reg_data['salary'][reg_data['country_id'] == 'LVA'] = 11927.88

# https://etateach.com/teacher-salaries-around-the-world.html#Mexico
reg_data['salary'][reg_data['country_id'] == 'MEX'] = 16044

# https://etateach.com/teacher-salaries-around-the-world.html#Norway
reg_data['salary'][reg_data['country_id'] == 'NOR'] = 44189

reg_data
```

```{r}
# https://etateach.com/teacher-salaries-around-the-world.html#New_Zealand
reg_data['salary'][reg_data['country_id'] == 'NZL'] = 48949
reg_data['expenditure_percapita'][reg_data['country_id'] == 'NZL'] = 17079.105

# https://etateach.com/teacher-salaries-around-the-world.html#Poland
reg_data['salary'][reg_data['country_id'] == 'POL'] = 18068

# https://etateach.com/teacher-salaries-around-the-world.html#Portugal
reg_data['salary'][reg_data['country_id'] == 'PRT'] = 15358.53

# https://etateach.com/teacher-salaries-around-the-world.html#Russia
reg_data['salary'][reg_data['country_id'] == 'RUS'] = 15192

# https://etateach.com/teacher-salaries-around-the-world.html#Saudi_Arabia
reg_data['salary'][reg_data['country_id'] == 'SAU'] = 40224

# https://etateach.com/teacher-salaries-around-the-world.html#Turkey
reg_data['salary'][reg_data['country_id'] == 'TUR'] = 5871.78
reg_data['expenditure_percapita'][reg_data['country_id'] == 'TUR'] = 3062.756

reg_data

```

```{r}
for(i in 3:ncol(reg_data)){
  reg_data[,i] <- as.numeric(reg_data[,i])
}
reg_data$expenditure_percapita <- round(reg_data$expenditure_percapita, 3)
reg_data$gov_expenditure <- round(reg_data$gov_expenditure, 3)
reg_data$net_user <- round(reg_data$net_user, 3)
reg_data
```

```{r}
write.csv(reg_data, "39countries_alldatacotttt.csv", sep = ";", dec = ".")
salary <- reg_data[, c('country_id', 'country_name', 'salary', 'expenditure_percapita')]
salary
gov_expenditures <- reg_data[, c('country_id', 'country_name', 'gov_expenditure')]
gov_expenditures
```

```{r}
write.csv2(salary, "39countries_salary.csv", sep = ";")
write.csv2(gov_expenditures, "39countries_govspendonedu.csv", sep = ";")
```


